Natural variation in teosinte at the domestication locus teosinte branched1 (tb1)

### 2014-01-16 manuscript.tex
edits to tex

\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage[pdftex]{graphicx}  
\usepackage{caption}
\usepackage{natbib}
\bibliographystyle{apalike}
\usepackage{color}
\usepackage{authblk}
\newcommand{\jri}[1]{\textcolor{blue}{ \emph{\scriptsize  #1}} }

@@

\author[1]{Laura Vann}
\author[1]{Thomas Kon\o}
\author[1]{Tanja Pyh\"aj\"arvi}
\author[1]{Matthew Hufford}
\author[1,2]{Jeffrey Ross-Ibarra\thanks{rossibarra@ucdavis.edu}}
\affil[1]{Department of Plant Sciences, University of California Davis}
\affil[2]{Center for Population Biology and Genome Center, University of California Davis}

\date{}

@@

\subsection*{ABSTRACT}

@@

\section*{Introduction}
\jri{plase redo sections not in all caps}

Domesticated crops and their wild progenitors provide an excellent system in which to study adaptation and genomic changes associated with human-mediated selection \cite{Ross-Ibarra et al 2007}. Perhaps the central focus of the study of domestication has been the identification of genetic variation underlying agronomically important traits such as fruit size and plant architecture \cite{Olsen and Gross 2010}. Additionally, many domesticates show reduced genetic diversity when compared to their wild progenitors, and an understanding of the distribution of diversity in the wild and its phenotypic effects has become increasingly useful to crop improvement \cite{Kovach and McCouch 2008}. But while some effort has been invested into understanding how wild alleles behave in their domesticated relatives, very little is known about the role that alleles found most commonly in domesticates play in natural populations of their wild progenitors.

@@

\section*{METHODS}

@@

\subsection*{Phenotyping 2}

@@

\section*{DISCUSSION}

@@

Given that the Hopscotch insertion has been estimated to predate the domestication of maize, it is not surprising that it is still segregating in populations of teosinte. However, in sampling numerous individuals from many teosinte populations our study provides greater insight into the distribution and prevalence of the Hopscotch in teosinte. While our findings are consistent with a previous study by Studer et al. (2011) in that we identified the Hopscotch allele segregating in teosinte, we find it at higher frequency than previously suggested \cite{Studer et al 2011}. Crop to wild introgression has previously been observed at domestication loci (\cite{Ellstrand et al 1999, Zhang et al 2009, Thurber et al 2010, Baack et al 2008, Hubner et al 2012, Wilkes et al 1977, Van Heerwaarden et al 2011, Barrett 1983}), but our results are more consistent with Hufford et al. (2013) who found resistance to introgression from maize into teosinte \cite{Hufford et al 2013}. Furthermore, \jri{all citations, even citations like these need to reference the bibtex file. check out the difference betweetn cite, citet, and citep as commands.} Hufford et al. (2013) showed that domestication loci, such as \emph{tb1}, are particularly resistant to introgression in both directions of gene flow (i.e., maize to teosinte and teosinte to maize).

@@

\clearpage
\bibliography{refs}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage{color}
\usepackage[pdftex]{graphicx}  
%\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\renewcommand{\baselinestretch}{1.5}
\bibliographystyle{apalike}

\newcommand{\jri}[1]{\textcolor{blue}{ \emph{\scriptsize  #1}} }

@@

\author[1]{Laura Vann}
\author[1]{Thomas Kono}
\author[1]{Tanja Pyh\"aj\"arvi}
\author[1]{Matthew Hufford}
\author[1,2]{Jeffrey Ross-Ibarra\thanks{rossibarra@ucdavis.edu}}
\affil[1]{Department of Plant Sciences, University of California Davis}
\affil[2]{Center for Population Biology and Genome Center, University of California Davis}

@@

\clearpage

\subsection*{Abstract}

@@

\clearpage

\section*{Introduction}

Domesticated crops and their wild progenitors provide an excellent system in which to study adaptation and genomic changes associated with human-mediated selection \cite{Ross-Ibarra et al 2007}. Perhaps the central focus of the study of domestication has been the identification of genetic variation underlying agronomically important traits such as fruit size and plant architecture \cite{OlsenGross2010}. \jri{I believe you need to remove spaces from the bibtex citation names.  See how this OlsenGross2010 works but the others don't? should be able to work with whitespace but i can't figure out why not.}  Additionally, many domesticates show reduced genetic diversity when compared to their wild progenitors, and an understanding of the distribution of diversity in the wild and its phenotypic effects has become increasingly useful to crop improvement \cite{Kovach and McCouch 2008}. But while some effort has been invested into understanding how wild alleles behave in their domesticated relatives, very little is known about the role that alleles found most commonly in domesticates play in natural populations of their wild progenitors.

@@

\section*{Methods}

@@

\subsubsection*{Phenotyping 2}

@@

\section*{Discussion}

@@

Given that the Hopscotch insertion has been estimated to predate the domestication of maize, it is not surprising that it is still segregating in populations of teosinte. However, in sampling numerous individuals from many teosinte populations our study provides greater insight into the distribution and prevalence of the Hopscotch in teosinte. While our findings are consistent with a previous study by Studer et al. (2011) in that we identified the Hopscotch allele segregating in teosinte, we find it at higher frequency than previously suggested \cite{Studer et al 2011}. Crop to wild introgression has previously been observed at domestication loci (\cite{Ellstrand et al 1999, Zhang et al 2009, Thurber et al 2010, Baack et al 2008, Hubner et al 2012, Wilkes et al 1977, Van Heerwaarden et al 2011, Barrett 1983}), but our results are more consistent with Hufford et al. (2013) who found resistance to introgression from maize into teosinte \cite{Hufford et al 2013}. Furthermore, \jri{all citations, even citations like these need to reference the bibtex file. check out the difference betweetn cite, citet, and citep as commands. see \url{http://merkel.zoneo.net/Latex/natbib.php} for details} Hufford et al. (2013) showed that domestication loci, such as \emph{tb1}, are particularly resistant to introgression in both directions of gene flow (i.e., maize to teosinte and teosinte to maize).

@@

\clearpage
\bibliography{refs,bob}
